Covariates analysis of MSBB RNASeq data

### 2016-01-04 code/Rmd/MSSM_RNASeq.Rmd
Minor changes in MSSB RNASeq covariates code

COVARIATES <- dplyr::mutate(COVARIATES, TISSUE.Dx = paste(TISSUE,Dx,sep='.'))
COVARIATES$TISSUE.Dx <- factor(COVARIATES$TISSUE.Dx)
```
Covariate correlation
```{r covariates.correlation, fig.width=10, fig.height=10}
COVARIATES.CORRELATION = getAssociationStatistics(COVARIATES, PVAL = 1)
ggheatmap.show(COVARIATES.CORRELATION$plot, col.width=0.3, row.width=0.15)
```
### Normalisation (with NULL)
Initial normalisation usign voom (with NULL design)
```{r initial.voom.normalisation}
# Initial normalisation of gene expression
VOOM.GENE_EXPRESSION = voom(PROCESSED_COUNTS$filteredExprMatrix, design=NULL, plot=T)

@@

```{r residualSigCovars.manual, fig.width=15, fig.height=8}
residualSigCovars[["PC_res"]][[1]]$plotData
```

```{r varsToAddBack}
# Add variable of interest back to the residuals
varsToAddIn = c("TISSUE.DxBM_10.AD", "TISSUE.DxBM_10.Control", "TISSUE.DxBM_22.AD",
                "TISSUE.DxBM_22.Control", "TISSUE.DxBM_36.AD","TISSUE.DxBM_36.Control")
RESIDUAL.GENE_EXPRESSION = RESIDUAL.GENE_EXPRESSION + 
  VOOM.ADJUSTED.FIT$coefficients[,varsToAddIn] %*% t(DM1$design[,varsToAddIn])
```

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE}
# Code
CODE <- Folder(name = "MSBB RNASeq", parentId = parentId)
CODE <- synStore(CODE)

# Expression
expr = rownameToFirstColumn(RESIDUAL.GENE_EXPRESSION, 'EnsembleIDs')
write.table(expr, file='expression.tsv', sep = '\t', row.names=F, quote=F)
obj = File('expression.tsv', 
           name = 'Voom Adjusted Weighted Residual Expression', 
           parentId = CODE$properties$id)
obj = synStore(obj,
               used = ALL_USED_IDs, 
               activityName = activityName, 
               executed = thisFile, 
               activityDescription = activityDescription)

>>>>

COVARIATES <- dplyr::mutate(COVARIATES, TISSUE.Dx = paste(TISSUE,Dx,sep='.'))
COVARIATES$TISSUE.Dx <- factor(COVARIATES$TISSUE.Dx)
rownames(COVARIATES) <- rownames(METADATA)
```
Covariate correlation
```{r covariates.correlation, fig.width=10, fig.height=10}
COVARIATES.CORRELATION = getAssociationStatistics(COVARIATES, PVAL = 1)
ggheatmap.show(COVARIATES.CORRELATION$plot, col.width=0.3, row.width=0.15)
```
### Normalisation (with NULL)
Initial normalisation usign voom (with NULL design)
```{r initial.voom.normalisation}
# Initial normalisation of gene expression
VOOM.GENE_EXPRESSION = voom(PROCESSED_COUNTS$filteredExprMatrix, design=NULL, plot=T)

@@

```{r residualSigCovars.manual, fig.width=15, fig.height=8}
residualSigCovars[["PC_res"]][[1]]$plotData
```
### Residual calculation
Calculate weighted residuals and add back "TISSUE.Dx" to the residuals
```{r varsToAddBack}
# Add variable of interest back to the residuals
varsToAddIn = c("TISSUE.DxBM_10.AD", "TISSUE.DxBM_10.Control", "TISSUE.DxBM_22.AD",
                "TISSUE.DxBM_22.Control", "TISSUE.DxBM_36.AD","TISSUE.DxBM_36.Control")
RESIDUAL.GENE_EXPRESSION = RESIDUAL.GENE_EXPRESSION + 
  VOOM.ADJUSTED.FIT$coefficients[,varsToAddIn] %*% t(DM1$design[,varsToAddIn])
```

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "MSBB RNASeq", parentId = parentId)
CODE <- synStore(CODE)

# Expression
expr = rownameToFirstColumn(RESIDUAL.GENE_EXPRESSION, 'EnsembleIDs')
write.table(expr, file='expression.tsv', sep = '\t', row.names=F, quote=F)
obj = File('expression.tsv', 
           name = 'Voom Adjusted Weighted Residual Expression (Tissue.Dx added)', 
           parentId = CODE$properties$id)
obj = synStore(obj,
               used = ALL_USED_IDs, 
               activityName = activityName, 
               executed = thisFile, 
               activityDescription = activityDescription)
